RCloud: Integrated Visualization, Analysis, Development, and Deployment

### 2015-01-23 conclusion.tex
yes
stuff

We described the motivation introducing web technologies
for searching, collaborating, recommending, publishing
reusable notebooks as part of the visual analytics process.
We implemented these ideas in the RCloud prototype.
Rcloud assists software development and release using
an approach similar to DevOps in web services.
Experience with the prototype provided evidence that
data science teams, and the organizations in which they work,
benefit from having such capabilities.

Future work will address cross-language development,
source code analysis, richer recommendation techniques,
and improvements to the HTML5 front end.

>>>>

We presented a case for introducing web technologies
for searching, collaborating, recommending, publishing
reusable notebooks to the visual analytics process.
We implemented these ideas in the RCloud prototype.
RCloud assists software development and release using
an approach similar to DevOps in web services.
Experience with the prototype provided evidence that
data science teams, and the organizations in which they work,
benefit from having such capabilities.

Reasonable next steps are to support cross-language development,
source code analysis, richer recommendation techniques, and
improvements to the HTML5 human interface.

### 2015-01-23 discussion.tex
notes
stuff

Experience with deploying RCloud in a community of data analysts
(``hackers'') has provided some insight about how the proposed
requirements were met and to what extent they were appropriate.
This experience may be informative to researchers and implementers
of future systems supporting collaborative visual analytics.

Returning to Heer and Agrawala's design considerations, our experience
both underscores the relevance of their proposals and indicates areas
for further exploration. We briefly examine these aspects of the
visual analytics environment.

>>>>

\carlos{All this stuff needs to appear in the paper much earlier.}

Experience with deploying RCloud in a community of data analysts
(``hackers'') has provided some insight about whether the proposed
requirements were appropriate, and how well they were met.
\stephen{The term {\it hackers} may be too tainted for us to use.}
% I know the following is true but also feel we need to let the work speak for itself. SCN
%This experience may be informative to researchers and implementers
%of future systems supporting collaborative visual analytics.

Returning to Heer and Agrawala's design considerations, our experience
underscores the relevance of their proposals, and indicates areas
for further exploration. We briefly examine these aspects of the
visual analytics environment.

### 2015-01-23 introduction.tex
stuff

% What's the area
Consider the emerging role of a data science team within an
organization today \cite{Keim:2008:VAS}.
%
% How do people do it today?
Individual data scientists and statisticians usually work on loosely
related problems, and must devise effective ways to share their findings
and move results from exploratory data analysis to automated diagnostics
and reports that are deployed for wider consumption.
They generally rely on a patchwork of resources shared informally,
or at best, through systems that attack individual tasks or functions
in the data analysis workcycle. % might cite information visualization reference model or pirolli/card

% Why does this not work?
There are two problems with the current practice. First, there are
gaps in the workflow: Exploratory Data Analysis (EDA) is done with one
set of tools, and automated reports and deployments with another. This
makes transferring results between EDA and production (in both
directions) slow, expensive, and error-prone. Coordination is done
through meetings and may take months to carry out.

Second, EDA environments often assume a single-developer perspective,
while data scientist teams could greatly benefit from convenient searching
and sharing of scripts, data sets, data feeds, experiments, annotations,
and automated analyses and recommendations. These capabilities have had
tremendous impact on information retrieval in general but are well
beyond what existing visual analytics environments provide, or what
is found in today's repositories and version control
systems.\cite{Koren:2009:FIT}

>>>>

% What's the area
Consider the emerging role of a data science team within an
organization today \cite{Keim:2008:VAS}.
%
% How do people do it today?
Individual data scientists and statisticians usually work on loosely
related problems, and must devise effective ways to share their findings
and move results from exploratory data analysis to automated reports and
diagnostics that are deployed for wider consumption.
They generally rely on a patchwork of resources shared informally,
or at best, through systems that attack individual tasks or functions
in the data analysis workcycle. % might cite information visualization reference model or pirolli/card

% Why does this not work?
There are two problems with the current practice. First, there are
gaps in the workflow: Exploratory Data Analysis (EDA) is done with one
set of tools, and automated reports and deployments with another. This
makes transferring results between EDA and production slow, expensive,
and error-prone, in both directions. Coordination is done through meetings
and may take months to carry out.

Second, EDA environments often assume a single-developer perspective,
while data scientist teams could greatly benefit from convenient searching
and sharing of scripts, data sets, data feeds, experiments, annotations,
and automated analyses and recommendations. These capabilities have had
extraordinary impact on information retrieval in general, but are well
beyond what existing visual analytics environments provide, or what
is found in today's repositories and version control
systems.\cite{Koren:2009:FIT}

### 2015-01-23 paper.tex
yes
stuff

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Individual data scientists and statisticians usually
  work on loosely related problems, and must devise effective ways to
  share their findings and move results from exploratory data analysis
  into automated diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, EDA environments often assume a single-developer perspective,
  while data scientist teams would get much benefit from easier sharing
  of scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide. We contribute and justify the following three
  requirements for systems built to support current data science teams
  and users: \emph{technology transfer}, \emph{coexistence}, and
  \emph{discoverability}. In addition, we contribute the design and
  implementation of RCloud, a system that supports the requirements
  collaborative data analysis, visualization and web deployment. We
  discuss the design decisions, tradeoffs and limitations, and compare RCloud
  to other current proposals.
  \carlos{RCloud has been in production use for more than a year and has about one hundred active users. We will discuss the adoption issues and etc etc.}
} % end of abstract

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.95\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
    \carlos{Come up with caption for this. The story is: hackers/scripters work in the middle (and bottom-right), rest of organization has automatic access to their work on left and top-right.}
  }
% \vspace{-.5em}
}

>>>>

%% Abstract section.
\abstract{ Consider the emerging role of data science teams within
  organizations. Individual data scientists and statisticians usually
  work on loosely related problems, and must devise effective ways to
  share their findings and move results from exploratory data analysis
  into automated diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, EDA environments often assume a single-developer perspective,
  while data scientist teams would get much benefit from easier sharing
  of scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide. We contribute and justify the following three
  requirements for systems built to support current data science teams
  and users: \emph{technology transfer}, \emph{coexistence}, and
  \emph{discoverability}. In addition, we contribute the design and
  implementation of RCloud, a system that supports the requirements
  collaborative data analysis, visualization and web deployment. We
  discuss the design decisions, tradeoffs and limitations, and compare RCloud
  to other current proposals.
  \carlos{RCloud has been in production use for more than a year and has about one hundred active users. We will discuss the adoption issues and etc etc.}
} % end of abstract

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.95\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
    \carlos{Come up with caption for this. The story is: hackers/scripters work in the middle (and bottom-right), rest of organization has automatic access to their work on left and top-right.}
    \stephen{An overview of RCloud. a) Workbooks of published experiments and production applications are visible and searchable by all authorized users in an organization b) Data scientists create, publish and anotate workbooks with support for sharing and recommendation c) Workbooks can be parameterized and deployed as production services}
  }
% \vspace{-.5em}
}
